Indicators for Ecosystem Condition in Norway

### 2022-08-02 indicators/indicatorTest.Rmd
template

@@

>>>>

# (PART\*) INDICATORS {-}

@@

<br />

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
```

<!-- Fill in which ecosystem the indicator belongs to, as well as the ecosystem characteristic it should be linked to. It's OK to use some Norwegian here -->

```{r, echo=F}
Ecosystem <- "Skog og fjell"
Egenskap  <- "Primærproduksjon"
ECT       <- "Structural state characteristic"
Contact   <- "Anders Kolstad"
```

```{r, echo=F}
metaData <- data.frame(Ecosystem,
                       "Økologisk egenskap" = Egenskap,
                       "ECT class" = ECT)
knitr::kable(metaData)
```

<br />
<br />

<hr />

<!-- Documenting you work below. Dtaa can be stores on NINA server, harvested using API or similar, or if it is not too big, stored under /data/ on this repository -->
